### 2023-12-30 chapters/qcd.tex
New year commit

\chapter{Quantum Chromodynamics:\\A Picture Book}

>>>>

\chapter[Quantum Chromodynamics: A Picture Book]{Quantum Chromodynamics:\\A Picture Book}
\markboth{\bf Chapter \thechapter: Quantum Chromodynamics}{}

The discovery of hadronic jets in high energy particle collisions is one of the most important milestones in human understanding of the strong nuclear force and of the microscopic universe.
%
Jets were originally predicted \cite{}, and later measured \cite{}, as collimated sprays of hadronic radiation produced in high energy collisions involving the strong interaction.
%
The explosion of experimental, phenomenological, and theoretical study of jets that followed has solidified Quantum Chromodynamics (QCD) as our fundamental theory of the strong nuclear force.
%
The use of jets as experimental and theoretical proxies for quarks and gluons -- the fundamental particles described by QCD -- has facilitated an unprecedented study and understanding of the physical properties of the Standard Model of particle physics (SM) and of the mathematical structure of quantum field theory (QFT).
%
It is not an exaggeration to say that the discovery of jets has been one of the most important developments in the history of our study of the natural world.

% ==============================================
\section{Picture Book}
% ==============================================
\sam{Several cartoons associated with the concepts in the paper.}

Explain concepts easily and explain why they are hard.

Mention split between perturbative and non-perturbative.

Mention what I don't mention and why.

% -----------------------------------
% Particles Section:
% -----------------------------------
\begin{sourcefigure}[ht]
    % Figure graphics
    \centering
    % \includegraphics[width=\textwidth]{figures/tempfig}

    % Caption
    \caption{
        \sam{Particles and interactions}
    }

    % Figure Label
    \label{fig:picturebook_particles}
\end{sourcefigure}

% -----------------------------------
% Jets Section:
% -----------------------------------
\begin{sourcefigure}[ht]
    % Figure graphics
    \centering
    % \includegraphics[width=\textwidth]{figures/tempfig}

    % Caption
    \caption{
        \sam{Particles inside particles and jets}
    }

    % Figure Label
    \label{fig:picturebook_jets}
\end{sourcefigure}

% -----------------------------------
% Substructure Section:
% -----------------------------------
\begin{sourcefigure}[ht]
    % Figure graphics
    \centering
    % \includegraphics[width=\textwidth]{figures/tempfig}

    % Caption
    \caption{
        \sam{Jet substructure and jet grooming}
    }

    % Figure Label
    \label{fig:picturebook_substructure}
\end{sourcefigure}

% -----------------------------------
% Event Shapes Section:
% -----------------------------------
\begin{sourcefigure}[ht]
    % Figure graphics
    \centering
    % \includegraphics[width=\textwidth]{figures/tempfig}

    % Caption
    \caption{
        \sam{Event shapes}
    }

    % Figure Label
    \label{fig:picturebook_eventshapes}
\end{sourcefigure}

% ==============================================
\section{Outline}
% ==============================================
% Outline:
%   Buildup
%     Big picture context
%     Narrow down towards the part of the field where this is relevant
%   Introduce project:
%     In this paper we...
%    Any additional details for basic picture
%   Elaboration
%     Utility or necessity of the project
%   Outline of paper

%=======================
% Buildup
%=======================
% Big picture context

Narrow down towards the part of the field where this is relevant

%=======================
% Introducing project:
%=======================
% In this paper we...

Any additional details for basic picture

%=======================
% Elaboration
%=======================
Utility or necessity of the project

%=======================
% Outline of the paper
%=======================
The rest of the paper proceeds as follows:
%
\sam{Sections}

We give concluding thoughts and avenues for future exploration in \Sec{Conclusions}.

\sam{Mention of Appendices}

\sam{Mention of Problems}
